---
title: "Cross Validation"
author: "Yue Liu"
date: '`r format(Sys.time(), "%Y-%m-%d")`'
output: github_document

---

when you have lots of possible variable, you have to choose which ones will fo in your model.

For nested models, you have tests [you have to be worried about multiple comparisons and "fishing"]

For non-nested models, you don't have tests[AIC/ BIC / etc are traditional tools; Balance goodness of fit with "complexity"]

randomly split data into "training" and "testing"

evaluate using root mean square error

Refinements and vatiations: Individual training/testing splits are subjects to randomness; Repeat the process(illustrates variability in prediction accuracy)

Cross validation is general

can use to compare candidate models that are all "traditional"

comes up a lot in "modern" methods (automed variable selection (lasso), additive models, regression trees)

```{r setup, include=FALSE}
library(tidyverse)
library(modelr)
library(mgcv)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Simulate data

```{r}
nonlin_df = 
  tibble(
    id = 1:100,
    x = runif(100, 0, 1),
    y = 1 - 10 * (x - .3) ^ 2 + rnorm(100, 0, .3)
  )
```

Look at the data 

```{r}
nonlin_df %>% 
  ggplot(aes(x = x, y = y)) + 
  geom_point()
```

## Cross validation -- by hand

get training and testing datasts

```{r}
train_df = sample_n(nonlin_df, size = 80) #%>% arrange(id)
test_df = anti_join(nonlin_df, train_df, by = "id") #%>% arrange(id)
```

Fit three models 

```{r}
linear_mod = lm(y ~ x, data = train_df)
smooth_mod = gam(y ~ s(x), data = train_df)
wiggly_mod = gam(y ~ s(x, k = 30), sp = 10e-6, data = train_df)
```

```{r}
train_df %>% 
  add_predictions(linear_mod) %>% #add a column of fitted values
  ggplot(aes(x = x, y = y)) + 
  geom_point() + 
  geom_line(aes(y = pred), color = "red")

train_df %>% 
  add_predictions(smooth_mod) %>% #add a column of fitted values
  ggplot(aes(x = x, y = y)) + 
  geom_point() + 
  geom_line(aes(y = pred), color = "red")

train_df %>% 
  add_predictions(wiggly_mod) %>% #add a column of fitted values
  ggplot(aes(x = x, y = y)) + 
  geom_point() + 
  geom_line(aes(y = pred), color = "red")
```

add prediction for multiple models

```{r}
train_df %>% 
  gather_predictions(linear_mod, smooth_mod, wiggly_mod) %>% 
  ggplot(aes(x = x, y = y)) + 
  geom_point() + 
  geom_line(aes(y = pred), color = "red") +
  facet_grid(.~ model)
```

Look at prediction accuracy 

```{r}
rmse(linear_mod, test_df)
rmse(smooth_mod, test_df)
rmse(wiggly_mod, test_df)
```

